---
title: "615 report"
author: "Ruiyi Lian"
date: "November 11, 2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(usmap)
```

### Input&Intro Data

<h4>The data is about the disaster distribution in the United State.

```{r}
r <- read_csv("C:/Users/LXD/Documents/R/615 mapping/report/r(1).csv")
head(r)
```

<h4> For more information of the data:
### Data Cleaning

First of all, we need to select the variable we need. They are disasterNumber which helps us identify which
disaster we are looking, county and state which help us locate where these disaster happened, incident type which helps us know what kinds of disaster it was, and state number code and county code which help us draw the map.

```{r}
data<-r%>%group_by(disasterNumber,county,state)%>%summarise(projectAmount=sum(projectAmount),countyCode=max(countyCode),stateNumberCode=max(stateNumberCode),incidentType=max(incidentType),.groups = 'drop')
data1<-data%>%group_by(county)%>%summarise(projectAmount=sum(projectAmount),countyCode=max(countyCode),stateNumberCode=max(stateNumberCode),incidentType=max(incidentType),state=max(state),.groups = 'drop')
head(data1)
```


### MAPPing

Here is examples for our data visualization on US Map.

#### Based on DisasterNumber

Let's take #1264 disaster for example.

```{r}
data2<-data[data$disasterNumber == 1264,]

#based on us map
plot_usmap(data = data2, values = "projectAmount", color = "red") + 
      scale_fill_continuous(
        low = "blue", high = "red", name = "Disaster", label = scales::comma
      ) + labs(title = "US Disaster") + theme(legend.position = "right")

#based on State map
a<-data2$state
data2<-data2%>%filter(county != "Statewide")
    data2<-data2 %>% rowwise %>% mutate(fips = 1000*stateNumberCode+countyCode)
plot_usmap(regions = "county", data = data2, values = "projectAmount",include = a ,color = "red") + 
      scale_fill_continuous(
        low = "blue", high = "red", name = "Disaster", label = scales::comma
      ) + labs(title = "US Disaster") + theme(legend.position = "right")
```

#### Based on State

Let's take PA as an example

```{r}
data3<-data1[data1$state == "Pennsylvania",]

#Based on the US MaP
data3_1<-data3%>%group_by(state)%>%summarise(projectAmount=sum(projectAmount),countyCode=max(countyCode),stateNumberCode=max(stateNumberCode),incidentType=max(incidentType),.groups = 'drop')
    
plot_usmap(data = data3_1, values = "projectAmount", color = "red") + 
      scale_fill_continuous(
        low = "blue", high = "red", name = "Disaster", label = scales::comma
      ) + labs(title = "US Disaster") + theme(legend.position = "right")
#Based on the state Map
a<-data3$state
data3_2<-data3%>%filter(county != "Statewide")
    data3_2<-data3_2 %>% rowwise %>% mutate(fips = 1000*stateNumberCode+countyCode)
plot_usmap(regions = "county", data = data3_2, values = "projectAmount",include = a ,color = "red") + 
      scale_fill_continuous(
        low = "blue", high = "red", name = "Disaster", label = scales::comma
      ) + labs(title = "US Disaster") + theme(legend.position = "right")
```

#### Based on Incident Type

Let's take Biological as an example

```{r}
data4<-data1[data1$incidentType == "Biological",]

#Based on the US MaP
data4_1<-data4%>%group_by(state)%>%summarise(projectAmount=sum(projectAmount),countyCode=max(countyCode),stateNumberCode=max(stateNumberCode),incidentType=max(incidentType),.groups = 'drop')
plot_usmap(data = data4_1, values = "projectAmount", color = "red") + 
      scale_fill_continuous(
        low = "blue", high = "red", name = "Disaster", label = scales::comma
      ) + labs(title = "US Disaster") + theme(legend.position = "right")
#Based on the state Map
a<-data4$state
data4_2<-data4%>%filter(county != "Statewide")
    data4_2<-data4_2 %>% rowwise %>% mutate(fips = 1000*stateNumberCode+countyCode)
plot_usmap(regions = "county", data = data4_2, values = "projectAmount",include = a ,color = "red") + 
      scale_fill_continuous(
        low = "blue", high = "red", name = "Disaster", label = scales::comma
      ) + labs(title = "US Disaster") + theme(legend.position = "right")
```
